Beyesian Inference for Decision Making under COVID-19: A case study

### 2020-05-29 out/paper.Rmd
Corrección LaTex

Although the normal parametrization is convenient for its simplicity, it should stand out to any statistician that there is a major problem choosing the gaussian family because $\theta$ $ \epsilon$ $ \Theta = [ 0, \infty ]$ and under the normality assumption $\Theta =  [- \infty, \infty]$. For now, our way around will be to truncate such $N(\hat{\theta}, \hat{\sigma^2})$ and redistribute tail density [^1].

>>>>

Although the normal parametrization is convenient for its simplicity, it should stand out to any statistician that there is a major problem choosing the gaussian family because $\theta$ $\epsilon$ $\Theta = [ 0, \infty ]$ and under the normality assumption $\Theta =  [- \infty, \infty]$. For now, our way around will be to truncate such $N(\hat{\theta}, \hat{\sigma^2})$ and redistribute tail density [^1].
